---
Last-Updated: 12-24-2024
Created: 02-12-2024
format: gfm
editor: source
editor_options:
  chunk_output_type: console
chunk_output_type: console
---

# Mouse Behavior Graphs

This project will print multiple graphs for various tests of mouse behavior. The main purpose
of this code is to be re-usable, even when new data is added (whether that be new mice, or 
new genotypes). For publication quality graphs, it would be more appropriate to create a 
new file of code and render those specific graphs verbosely. 

This is the code used by BehaviorGraphs v2.0 ([github](https://github.com/JeffreyDeanBrown/BehaviorGraphs))

The use-case for this code is very narrow, at this point it's really just for the author to practice.

### example plot:

```{r, message=FALSE, results='hide', eval=TRUE, echo = FALSE}
library(openxlsx) 
library(tidyverse)
options(dplyr.summarise.inform = FALSE)
library(glue) 
library(ggformula) 
library(vctrs) 
library(snakecase) 
library(gridExtra)
library(devtools)
library(Hmisc)
library(magrittr)
install_github(repo = 'https://github.com/JeffreyDeanBrown/BehaviorGraphs',
               subdir = "BehaviorGraphs")
library(BehaviorGraphs)

organize_data(spreadsheet_name = 'example_sheets/Behavior Data 01-08-24.xlsx') %>%
  label_the_data() %>%
    plot_default_graphs()

genotype_group %>% subset(subset = genotype_group$group_sex == 'pFlp Hetero (Female)', select = grip_plot) %>% as.list
```

## setup

```{r, message=FALSE, results='hide', eval=FALSE}

library(openxlsx) 
library(tidyverse)
options(dplyr.summarise.inform = FALSE)
library(glue) 
library(ggformula) 
library(vctrs) 
library(snakecase) 
library(gridExtra)
library(devtools)
library(Hmisc)
library(magrittr)
install_github(repo = 'https://github.com/JeffreyDeanBrown/BehaviorGraphs',
               subdir = "BehaviorGraphs")
library(BehaviorGraphs)


# setwd("")

print("Done with Setup")

```





## Create and print the default graphs

```{r, message=FALSE, results='hide', eval=FALSE}

genotype_of_the_day <- "OSKO"        # either a string or a vector of strings
filename_of_the_day <- "OSKO.pdf"    # you need one filename for each genotype

organize_data(spreadsheet_name = 'example_sheets/Behavior Data 01-08-24.xlsx') %>%
  label_the_data() %>%
    plot_default_graphs()

print_default_plots()

```





## Customize a set of graphs

This essentially just subsets your data to a list of genotypes you are interested in

```{r, message=FALSE, results='hide', eval=FALSE}

organize_data(spreadsheet_name = 'example_sheets/Behavior Data 01-08-24.xlsx') %>%
  label_the_data() %>%
    show_custom_options() # prints your genotypes_to_plot and graph_to_preview options

organize_data(spreadsheet_name = 'example_sheets/Behavior Data 01-08-24.xlsx') %>%
  label_the_data() %>%
    generate_custom_graphs(genotypes_to_plot = c("pFlp Homo (Male)", "OSKO Homo wSOD1M (Female)"),
                           graph_to_preview = "grip_plot")

```
